### 2020-01-31 wuhan.tex
adding bryan's comments

Finally, we incorporate all uncertainties by using posterior samples for $\mu_r$, $\mu_G$, and $\mu_\kappa$ to recalculate \Ro and compare it with the reported \Ro estimates.
We estimate the average \Ro to be 3.1 (95\% CI: 2.1--5.7).
While our pooled estimate of \Ro is similar to other reported values, our calculation gives wider confidence intervals than all of them.
This result does not imply that assumptions based on the pooled estimate are too weak;
we believe that this confidence interval accurately reflects the level of uncertainties present in the information that was available when these models were fitted.

@@

More broadly, disease modelers should always consider uncertainties in the data generating processes.
Process vs obs noise.

Our results indicate that the uncertainty in the estimates of the exponential growth rate $r$ matters the most.
However, as the epidemic progresses and more data becomes available, inference on epidemic trajectories will become more precise.
Uncertainty in the exponential growth rate will eventually decrease, 
and the effect of uncertainty in the mean generation time will become more important.

>>>>

Finally, we incorporate all uncertainties by using posterior samples for $\mu_r$, $\mu_G$, and $\mu_\kappa$ to recalculate \Ro and compare it with the reported \Ro estimates.
We estimate the average \Ro to be 3.1 (95\% CI: 2.1--5.7).
While our pooled estimate of \Ro is similar to other reported values, our calculation gives wider confidence intervals than all of them.
This result does not imply that assumptions based on the pooled estimate are too weak;
we believe that this confidence interval accurately reflects the level of uncertainties present in the information that was available when these models were fitted.
\swp{Bryan: any comment about why R0 isn’t at the lower end of previous estimates? (Guess someone might ask this)}

@@

More broadly, disease modelers should always consider different sources of uncertainties in the data generating process.
Two main sources are process error, which refers to stochasticity in the process of disease spread, and observation error, which often refers to imperfect reporting.

Our results indicate that the uncertainty in the estimates of the exponential growth rate $r$ matters the most.
However, as the epidemic progresses and more data becomes available, inference on epidemic trajectories will become more precise.
Uncertainty in the exponential growth rate will eventually decrease, 
and the effect of uncertainty in the mean generation time will become more important.
Furthermore,
